Preventing Runtime Errors of Redis at Compile Time

### 2015-11-20 paper.tex

\section{Conclusion and Related Work}
\paragraph{Acknowledgements}

>>>>

Redis also provides \emph{transactions}, another context for executing commands.
Redis trasanctions are atomic in the sense that, all commands in a transaction
 will executed sequentially, and no other requests issued by other clients will
 be served \textbf{in the middle}.\footnotemark In contrast, we cannot make such
 a guarantee in the ordinary context, which may destroy the assertions we made
 in types.

At the point of writing, transactions are not supported in our implementation.
 We are planning to add it in the future, and we are expecting that there
 wouldn't be much difficulties, since we've implemented a runtime type checker
 specifically targeting Redis transactions once, before we moved on to the
 types.

\section{Related Work}

While Redis can be viewed as a non-relational database system (although Redis
 seems reluctant to admit this in recent years), there also similar goals on
 relational database systems, trying to achieve a safer database interface by
 making them statically checked.
 \emph{HaskellDB}\cite{haskelldb}\cite{haskelldbimproved} expresses quries
 with relational algebra-like combinators, wrapped in phantom types. Or as
 examples, at first to demonstrate the power of dependent types in
 Agda\cite{pi}, and then with singletons in Haskell\cite{singletons}.

\section{Conclusions}

We have shown that how a embedded DSL with variable-bindings could be expressed
 in types and statically checked. With recent extensions to the language,
 Haskell is becoming more and more capable of dependently-typed programming, and
 it's not that scary as many (including me) would have thought.

\paragraph{Acknowledgements}
This material is based upon work supported by Institute of Information Science,
Academia Sinica under the Summer Internship Program of 2015.
